{{< var addns >}}

### 2024-09-23 addendum/Addendum_az.qmd
closed

---
title: "{{< var addns >}}"
subtitle: "{{< var addnl >}}"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

@@

```{r, echo=FALSE, out.width="80%", fig.cap=""}
pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
knitr::include_graphics(c(pa))
```

>>>>

---
title: "{{< var addns >}}"
subtitle: "{{< var addnl >}}"
# format:
#   revealjs: 
#     smaller: true
#     toc-depth: 1
#     toc: true 
# execute: 
#   cache: false
# footer: <https://lotariohw26.github.io/ManifoldDestiny/>
# output: 
#   html_document:
#     mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
# nocite: |
#   @*
---

@@

```{r, echo=FALSE, out.width="80%", fig.cap=""}
#pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
knitr::include_graphics(c(pa))
```
